---
title: "Use of the IlluminaHumanMethylationMSAmanifest"
author: "James W. MacDonald <jmacdon@uw.edu>"
date: '`r Sys.Date()`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Use of IlluminaHumanMethylationEPICv2manifest}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, echo = FALSE, message = FALSE}
library(knitr)
knitr::opts_chunk$set(
    error = FALSE,
    tidy  = FALSE,
    message = FALSE,
    warning = FALSE,
    fig.width = 6,
    fig.height = 6,
    fig.align = "center")
```

This package provides the manifest for the Illumina Human Methylation
MSA array, based on the [csv available on their support
site](https://support.illumina.com/content/dam/illumina-support/documents/downloads/productfiles/infiniummethylationscreening/MSA-48v1-0_20102838_A1.csv)
.

The script used to generate the manifest can be found in 
`r system.files("scripts", "manifest.R", package("IlluminaHumanMethylationMSAmanifest"))`.

Curently `minfi` will not automatically identify the array correctly,
so this must be set by hand. As an example:

```{r, eval = FALSE}

RGset <- read.metharray.exp(...)
annotation(RGset) <- list(array = "IlluminaHumanMethylationMSA",
                          annotation = "20a1.hg38")
                         

```

After setting the annotation, you can then process the `RGset` as
normal.

## Session info

```{r}

sessionInfo()

```
